---

Title: "DATA 607 Assignment 3"

output: html_document

---


***Gehad Gad***

***February 16th, 2020***

***Assignment 3***


```{r}
#Import libraries and/or Packages

#install.packages("tidyverse")
#install.packages("htmlwidgets")
library (stringr)
library (tidyverse)

```



***Question 1. Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset [https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/], provide code that identifies the majors that contain either "DATA" or "STATISTICS"***

```{r}
#Import the data into R.

majors <- read.csv ("https://github.com/fivethirtyeight/data/raw/master/college-majors/majors-list.csv")

```



```{r}
#Select the major(s)the contain the word DATA.

DATA = majors [grep ("DATA", majors$Major),]

```


```{r}
#Select the major(s)the contain the word STATISTICS.


STAT = majors [grep ("STATISTICS", majors$Major),]
```


```{r}
# Combine the two togther.

Data_Stat = rbind (DATA, STAT)
```


***Question 2. Write code that transforms the data below:***

[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"

[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  

[9] "elderberry"   "lime"         "lychee"       "mulberry"    

[13] "olive"        "salal berry"

***Into a format like this:***

c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")


```{r}
# We will create an array for all the item listed.

Array = array (c("bell pepper", "bilberry",   "blackberry",  "blood orange", 
"blueberry",  "cantaloupe" ,  "chili, pepper","cloudberry",  
"elderberry",   "lime", "lychee", "mulberry", 
"olive",    "salal berry"))

```


#Array

#[1] "bell pepper"   "bilberry"      "blackberry"    "blood orange" 
#[5] "blueberry"     "cantaloupe"    "chili, pepper" "cloudberry"   
#[9] "elderberry"    "lime"          "lychee"        "mulberry"     
#[13] "olive"         "salal berry" 


```{r}
#Create change the array to a vector and display the vector.

Vector = as.vector (Array)

dput(Vector)

```
 
 
 

***3 Describe, in words, what these expressions will match:***


***(.)\1\1***

```
() represents group one and the . represents a character other than /n or a space. Followed by numerical reference for group 1 then remerical reference for group 1

```


***"(.)(.)\\2\\1"***


```
The first dot represenes a character and the first () represents group one and the second () represent group two. The second dot is a character other than /n or a space, followed by another character. Followed by "2" then "1"


```

***(..)\1***

```
The () represents a group one. The .. represent a set of two characters are followed by a numerical reference of group 1.

```


***"(.).\\1.\\1"***

```
The () represents a group one. The two .. represent a character followed by "1" followed by a . which represents a character other than /n or a space followed by "1". 

```


***"(.)(.)(.).*\\3\\2\\1"***

```
The first dot represenes a character and the first () represents group one. The second () represent group two and the second dot is a character other than /n or a space, the third dot represenes a character and the third () represents group three followed by another character, "3", "2" then "1"

```


***Question 4.Construct regular expressions to match words that:***

***1. Start and end with the same character.***


```{r}

x1 <- c("sales", "saults", "scalps", "shapes", "scoop")

str_view (x1, "^s")

```




```{r}
str_view (x1, "s$")

```

***Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)***

```{r}
x2 <- c("shushing", "sharpshooter", "crosshatch", "sharp")
  
str_view (x2, " sh+")

str_count (x2, "sh")
  
  
```

***Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)***

```{r}

x3 <- c ("cheese", "deeper", "breeze", "Green")

str_view (x3, "ee+")

for (i in x3){count = str_count (i, "e")   
if (count >= 3){  print(i)}}

```




